---
title: "Probability"
author: "Muhammad Ahmad"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
```

### Exercise 1

Insert any text here.

```{r code-chunk-label}
glimpse(kobe_basket)
```

A streak of zero means the he missed the first shot denoted as "\|M\|" there are no hits in a streak of zero. A streak length of 1 means that he had one hit denoted as "\|HM\|" he made one basket a streak of one.

### Exercise 2

```{r}
kobe_streak <- calc_streak(kobe_basket$shot)

ggplot(data = kobe_streak, aes(x = length)) +
  geom_bar()
```

... Kobe's typical streak was zero meaning he missed most of the time. His longest streak is four meaning that he made four baskets in a row or got four hits.

### Exercise 3

```{r}
set.seed(6132111)
coin_outcomes <- c("heads", "tails")
sim_fair_coin <- sample(coin_outcomes, size = 100, replace = TRUE)
sim_fair_coin
```

```{r}
table(sim_fair_coin)
```

There are 43 heads and 57 tails in this sample.

### Exercise 4

```{r}
set.seed(6132112)
shot_outcomes <- c("H", "M")
sim_basket <- sample(shot_outcomes, size = 133, replace = TRUE, prob = c(0.45, 0.55))
sim_basket
```

```{r}
table(sim_basket)
```

### Exercise 5

```{r}
sim_streak <- calc_streak(sim_basket)
sim_streak
```

### Exercise 6

```{r}
ggplot(data = kobe_streak, aes(x = length)) +
  geom_bar()
```

The typical streak length for the simulated basket ball hit streak is 0 and its longest streak is 4 in 144 shots.

### Exercise 7

I would expect the simulation to run very similar if ran again since I added weights to the probabilities. Most likely the graph will stay the same shape and there will not be an additional column for a five hit streak.

### Exercise 8

Kobe Bryant's distribution of streak lengths are nearly identical to the simulated shooter streak lengths. The evidences these samples and models shows does suggest that if Kobe were to hit his first shot then there is a chance that he'll hit the next one
